---
title: "Linear Model"
author: "Daniella Sanchez"
date: "Summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

###Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

The y-axis is SIMS and the x-axis is ARMS. This plot shows that here is a positive linear correlation. 

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The evaluation for the line that fits this is SIMS is equal to -4.1 + .05 ARM
The formula needed is y= mx  + b to create the line.

# now add the model fit to our plot
  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

It looks like the value of the y-intercept would be around 1.



